---
title: "Diet Project_Github"
author: "Michelle C. Hsu"
date: "March 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
packages <- c("readxl", "tibble", "lubridate", "reshape2", "ggrepel", "car", "tidyverse", "dplyr", "ggplot2", "carData", "readr", "stringr")
lapply(packages, library, character.only = TRUE)
```

#####################################################
#     sub_nutri n =463 removed 2 outliers (std=3)   #
#####################################################
```{r}
sub_nutri <- nutri_dat[(!(nutri_dat$`DQ Calories`==5203.38) &
                       !(nutri_dat$`DQ Calories`==7900.39)),] 
  summary(sub_nutri$`DQ Calories`)
  length(unique(sub_nutri$Code)) #463
```
#####################################################
#              remove refdate and cal_age           # 
#####################################################
```{r}
sub_nutri <- subset(sub_nutri, select = -c(refdate,Calc_Age) ) 
sub_nutri$`Dem Years of Education` <- as.numeric(sub_nutri$`Dem Years of Education`)
```
#####################################################
#   master (n =409) after removed 54 offspring-pair #
#   drop refdate and Calc-Age;                      #
#   reorder Diet ID                                 #
#   reorder DQ calorie                              #
#   reorder DQ ID                                   #
#   sub_nutri includes 54-offspring from pair       #
#####################################################
```{r}
grep("Diet ID", colnames(sub_nutri)) #92
grep("DQ Calories", colnames(sub_nutri)) #212
grep("DQ ID", colnames(sub_nutri)) #246
grep("age_round", colnames(sub_nutri)) #305
#314 vars total
sub_nutri<- sub_nutri %>% select(Code:`Offspring Subtype`,`Diet ID`,`DQ Calories`, `DQ ID`,age_round, `Diet Beverage Beer`: `DQ Zn wo`)

names(sub_nutri) 
```
######################################################
#        master data has no 54 offspring pair        #
#          master_copy is a copy of master           #
#       (no transformation will be done in copy)     #
######################################################
```{r}
str(spouse_pairs) #data.frame
CODES_list <- spouse_pairs$Offspring #column CODES_list
str(CODES_list)
CODES_list_offspring <- as.list(CODES_list)
master <- sub_nutri[ ! sub_nutri$Code %in% CODES_list, ]
master_copy <- master
```
#################################################################
#                                TABLE 1                        #
#################################################################
################################################
#                       n                      #
################################################
```{r}
print('Total number of participants')
length(master$Code)
```
```{r}
print('Participants by offspring type')
table(master$`Offspring Type`) #280 offspring #129 control
```
################################################
#                     Age                      #
################################################
```{r}
print('mean age')
mean(master$age_round)
print('offspring type mean')
tapply(master$age_round,master$`Offspring Type`, mean)
print('offspring type standard deviation')
tapply(master$age_round,master$`Offspring Type`,  sd)
```
```{r}
boxplot(master$age_round ~ master$`Offspring Type`)
t.test(master$age_round ~ master$`Offspring Type`, mu = 0, alt = "two.sided", paired= F, var.equal = T) #0.491
```
################################################
#                 Calories                     #
################################################
```{r}
print('Caloric intake mean')
tapply(master$`DQ Calories`,master$`Offspring Type`, mean)
print('Caloric intake standard deviation')
tapply(master$`DQ Calories`,master$`Offspring Type`, sd)
```
```{r}
boxplot(master$`DQ Calories` ~ master$`Offspring Type`)
t.test(master$`DQ Calories` ~ master$`Offspring Type`, mu = 0, alt = "two.sided", paired= F, var.equal = T) 

hist(master$`DQ Calories`,breaks = "FD", xlab= "kcal/d", main= "Histogram of Calories")
```
################################################
#                  female                      #
################################################
```{r}
master %>%
  group_by(`Offspring Type`, `Dem Sex`) %>%
  summarise(n= n()) %>%
  mutate(freq = n/ sum(n))
```


```{r}
with(master, do.call(rbind, tapply(master$age_round, master$`Offspring Type`,function(x) c(M = mean(x), SD = sd(x)))))
```
```{r}
with(master, do.call(rbind, tapply(master$`DQ Calories`, master$`Offspring Type`,function(x) c(M = mean(x), SD = sd(x)))))
```

#################################################################
#                         remove var                            #
#################################################################
```{r}
master <-select(master, -c(`DQ Sach`))
```

#################################################################
#           master dataset select columns - diet                #
#                master with 201 variables                      #
#################################################################
```{r}
master <- master%>% select(Code:`Diet Veg Yams`) # var 163
names(master)
```
#####################################################
#      Replace 10 as NA (P on questionairre)        #
#####################################################
```{r}
master[,14:163][master[, 14:163] ==10] <- NA  
```

#####################################################
#            Fat categories are of concern          #
#####################################################
```{r}
master <-select(master, -c(`Diet Fat Added Sugar`:`Diet Fat Marg Tub`))
dim(master) #409 140 var 

sapply(master, function(x) sum(is.na(x)))
```

#####################################################
#                     Copy dataset                  #
#####################################################
```{r}
master_copy<- master
str(master_copy)
```
